\section{SiPM}
\label{sec:sipm}

SiPMs are pixelated photodetectors that are increasingly
used in contemporary high-energy physics experiments. Their compactness and form
factor make them ideal for many applications including calorimeters~\cite{Andreev:2004uy}
and charged particle detectors. They are also widely used for positron emission tomography
(PET) detectors together with LYSO scintillating crystals for medical imaging
purposes~\cite{Vandenberghe2016}, where new studies have improved the 
timing resolution below $100$~ps~\cite{LecoqTOFPET} and 
 can yield substantial improvements in spatial resolution and imaging 
 capabilities. The size of each SiPM device typically
ranges between $1\times 1$~$\mathrm{mm}^{2}$ and $6\times 6$~$\mathrm{mm}^{2}$,
with the size of each pixel ranging between $10$~$\mu$m to $50$~$\mu$m. SiPMs operate
at relatively high gain between $10^{5}$ and $10^{6}$, and have single photon detection
efficiency ranging from $10\%$ to $50\%$. 
%As each pixel operates in geiger mode, it is essentially a digital
%device. More than one photon impinging on a single pixel yields the same signal
%as a single photon impinging on that pixel. Therefore as the number of photons
%approaches the total number of pixels, the SiPM experiences a slow saturation as
%the signal response slowly becomes non-linear. Total saturation occurs 
%f the number of photons exceed the number of pixels in the device. 


SiPMs have a typical thermal dark count rate of about
$0.1$~MHz/$\mathrm{mm}^{2}$ at room temperature, which can be strongly decreased
when operated at lower temperatures. Typical operational temperatures range from
$20$$^{\circ}$C to $30$$^{\circ}$C, but can be as low as $-30$$^{\circ}$C. SiPMs have
been tested for the impact of radiation damage up to an equivalent neutron rate
of $2\times10^{14}$~$\mathrm{cm}^{2}$, and its performance have been shown to be
robust when operated at temperatures 
below~$5$$^{\circ}$C~\cite{SiPMIrradiated1,SiPMIrradiated2}. However, when operated
at the same temperature, the thermal dark count rate increases significantly
with large irradiation. The SiPMs used for our studies are Hamamatsu MPPC
S12571-010P and S12571-015P both of size $1\times1$~$\mathrm{mm}^{2}$, and
S12572-15C and S12572-25C both of size $3\times3$~$\mathrm{mm}^{2}$. These SiPMs
are chosen to allow us to study the impact of the size of the sensitive area and
the size of individual pixels on the timing performance. Studies of the impact
of SiPMs from alternative manufacturers are left for future work. Some relevant
details of the SiPM parameters are summarized in Table~\ref{tab:SiPMParameters}
below.

\begin{table}[!ht]
\begin{center}
\caption{Summary of performance parameters for SiPMs used in our studies.}
\label{tab:SiPMParameters}
\begin{tabular}{|c|c|c|c|c|}
\hline
Parameter & S12571-010C & S12571-015C & S12572-15C & S12572-25C\\
\hline
Photosensitive area              & $1\times1\mathrm{mm}^{2}$ & $1\times1\mathrm{mm}^{2}$ & $3\times3\mathrm{mm}^{2}$ & $3\times3\mathrm{mm}^{2}$\\
Pixel Pitch                            & $10\mu$m                             & $15\mu$m                             & $15\mu$m                              & $25\mu$m\\
Number of Pixels                 &  10000                                    &  4489                                      & 40000                                     & 14400                       \\
Dark Count Rate                  &  $0.1$~MHz                            &  $0.1$~MHz                            & $1$~MHz                                 & $1$~MHz                  \\
Gain                                    & $1.35\times10^{5}$                  & $2.3\times10^{5}$                & $2.3\times10^{5}$                 & $5.15\times10^{5}$  \\
Terminal Capacitance          & $35$~pF                                 & $35$~pF                                  & $320$~pF                                & $320$~pF                  \\
Spectral Response Range     & $320$-$900$~nm                  & $320$-$900$~nm                  & $320$-$900$~nm                   & $320$-$900$~nm     \\
Peak Sensitivity Wavelength & $470$~nm                              & $460$~nm                              & $460$~nm                               & $450$~nm               \\         
\hline
\end{tabular}
\end{center}
\end{table}