%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,1p]{elsarticle}
\usepackage{graphicx}
\pdfoutput=1
\biboptions{numbers,sort&compress}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{lineno}
\usepackage{hyperref}

%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

%% Title, authors and addresses
%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}


\journal{Nucl. Instrum. Meth. A}

\begin{document}
  
%\maketitle
%\flushbottom
\linenumbers

\begin{frontmatter}

\title{LYSO-based Precision Timing Detectors with SiPM Readout}

\author[1]{A.~Bornheim}
\author[2]{M.~H. Hassanshahi}
\author[1]{M.~Griffioen}
\author[1]{J.~Mao}
\author[1]{A.~Mangu}
\author[1]{C.~Pe$\tilde{\mathrm{n}}$a}
\author[1]{M.~Spiropulu}
\author[1]{S.~Xie \corref{cor}}
\ead{sixie@hep.caltech.edu}
\author[1]{Z.~Zhang}
\address[1]{California Institute of Technology, Pasadena, CA, USA}
\address[2]{Institute for Research in Fundamental Science, Tehran, Iran}
\cortext[cor]{Corresponding author}


\begin{abstract}
Particle detectors based on scintillation light are particularly well suited for precision timing applications with 
resolutions of a few 10 ps. The large primary signal and the fast initial rise of the scintillation
light result in very favorable signal-to-noise conditions with fast signals. In this paper we describe timing 
studies using a LYSO-based sampling calorimeter with wavelength-shifting capillary light extraction and silicon
photomultipliers as sensors. We study the contributions of various steps of the signal generation to 
the total time resolution, and demonstrate its feasibility as a radiation-hard technology for calorimeters
at high intensity hadron colliders.
\end{abstract}

\begin{keyword}
LYSO \sep Silicon Photomultiplier \sep Precision Timing \sep picosecond \sep scintillation \sep calorimeter
\end{keyword}

\end{frontmatter}

%% \linenumbers
%
%% main text
%
\input{introduction.tex}
%
%
\input{sipm.tex}  
%
%
\input{setup.tex}  
%
%

\section{Timing Measurements} 

While SiPMs feature a rise time around $1$~ns, slower than the rise time of MCPs, they
allow a very good timing performance for large, coherent signals. We present 
measurements of the timing performance for a
LYSO-based sampling calorimeter read out by wavelength-shifting light fibers
connected to SiPMs and discuss the impact of
the intrinsic timing performance of SiPMs on the calorimeter timing measurement
studied using light signals injected by a picosecond laser.

\input{beamtiming.tex}  
%
%
\input{lasertiming.tex}  
%
%

\section{Discussion} 
In our previous study~\cite{Anderson:2015gha}, we achieved
a time resolution of $110$~ps for $32$~GeV electromagnetic showers using
DSB-doped WLS fibers for light readout at both ends of the fiber. The two main
goals achieved in the present study are to confirm similar or slightly improved
timing performance using photodetectors that are economically scalable to
collider experiment size and WLS fibers that can maintain its transparency under
the harsh radiation conditions of the HL-LHC. Using commercially available SiPMs
that are economically scalable, we achieved a time resolution of $75$~ps
($40$~ps) for $50$~GeV ($200$~GeV) electromagnetic showers using DSB-doped WLS
fibers read out only at a single end of the fiber. This represents a $15\%$
improvement over the previous result, with the possibility for additional
improvement if light is read out from both ends of the WLS fibers. 

Using quartz capillaries filled with a DSB-based liquid wavelength-shifting
agent, specially designed to survive the high radiation environment of the
HL-LHC, we achieved a time resolution of $130$~ps ($75$~ps) for $50$~GeV
($200$~GeV) electromagnetic showers. The difference in timing resolution with
respect to the DBS-doped WLS fibers is solely due to degraded signal-to-noise
ratio as the light collection efficiency is worse for the quartz capillaries.
This result demonstrates feasibility towards a radiation-hard solution for the
future. Based on these results, we are optimistic that further work on improving
the optical coupling, improving the light collection efficiency of the quartz
capillaries by optimizing the dimensions and the composition of the liquid WLS
agent, and improving the noise properties of the SiPMs can yield further
improved timing performance. 

\input{summary.tex}  
%
%

\section{Acknowledgements} 
Supported by funding from California Institute of
Technology High Energy Physics under Contract DE-SC0011925 with the United
States Department of Energy. We thank the CERN test-beam facilities personnel for
excellent beam conditions during our test-beam time. We also thank Paolo
Meridiani and Francesco Micheli for their kind assistance on the setup of the
DAQ system at the test-beam. We greatly appreciate the collaboration with Randy
Ruchti who provided us with wavelength-shifting fibers doped with DSB as well as
quartz capillaries filled with liquid DSB wavelength shifter.
%
%
%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\bibliography{SiPMTiming}{}
\bibliographystyle{ieeetr} 

\end{document}
